---
title: "EDS212-Day5"
format: html
execute: 
  warning: false
editor_options: 
chunk_output_type: console
---

```{r}
#| message: false
#| include: false
# Load library ----
library(tidyverse)
```

`head()`, `tail()`, `dim()` on the `dplyr::starwars` data frame: 

```{r}
#| include: false
# Do some data exploration of the data ----

# First 6 rows of data set ----
head(starwars)

# Last 6 rows of data set ----
tail(starwars)

# Dimensions of documents, rows followed by columns ----
dim(starwars)

```

-Create a ggplot (scatterplot) pf character mass (y- axis) and height (x-axis)

-Update the color of the points so that color changes based on the value of `mass`
```{r}
#| echo: false
ggplot(starwars, aes(x = height, y = mass, color = mass, size = 100)) + 
  geom_point() + 
  labs(title = "Mass of Starwars Characters in Relation to Height", x = "Height (cm)", y = "Mass (kg)")
```

- Create a histogram of character heights 
- Update the fill color (`fill`)to purple and the outside border line (`color`) of each histogram bin to orange
- Update your code chunk options so that your code and output graph appear in the rendered doc (no warning or message)
```{r}
#| fig-cap: "Histogram showing disturbution of character height in Starwars"
#| fig-alt: "Text can be entered he for visually impared"
ggplot(starwars, aes(x = height)) + 
  geom_histogram(fill = "cyan4", color = "orange") + 
  labs(title = "Histogram of Character Height")
```

`df$col_name`

```{r}
sw_height_mean <- round(mean(starwars$height, na.rm = TRUE), 
                        digits = 3) 

```

The mean height (cm) of all Starwars characters is `r sw_height_mean`

```{r}
ggplot()

```



